Outdated and License-Violating Code on Stack Overflow

### 2017-10-10 cloverflow-tse/cloverflow.tex
Last update before flying.

\begin{table}[]
	\centering
	\caption{License mapping of  online clones (file-level)}
	\label{tab:license_abc}
	%\small
	\resizebox{\linewidth}{!}{
		\begin{tabular}{lp{2.2cm}lrrr}
			\toprule
			Type & Stack Overflow\newline (CC BY-NC-SA) & Qualitas & QS & EX & UD \\
			\midrule
			Compatible & Apache2 & Apache2 &  0 & 0  & 1\\
			License	& EPLv1 & EPLv1 &  1 & 0 & 1\\
			& Sun (proprietary) & Sun (proprietary) & 0 & 1 & 0\\
			& MIT-like & MIT-like & 0 & 1 & 0\\
			& No license & CC BY-NC-SA & 0 & 5 & 0 \\
			& No license & No license & 5 & 4 & 21 \\
			\midrule
			\multicolumn{3}{l}{Total} & 6 & 11 & 23 \\
			\midrule
			Incompat. & BSD3 & GPLv2+ & 0 & 0 & 1 \\
			License	& No license & AGPLv3/3+ & 1 & 0 & 2 \\
			& No license & Apache-2 & 41 & 6 & 23 \\
			& No license & BSD3 & 3 & 4 & 28 \\
			& No license & CDDL or GPLv2 & 1 & 0 & 58 \\
			& No license & CDDLv1 & 0 & 1 & 0 \\
			& No license & EPLv1 & 7 & 0 & 10 \\
			& No license & GPLv2/2+/3+ & 2 & 62 & 32 \\
			& No license & LGPLv2/2.1+/3+ & 24 & 0 & 32 \\
			& No license & MPLv1.1 & 0 & 0 & 1 \\
			& No license & spdxBSD3 & 0 & 0 & 10 \\
			& No license & SPLv1 & 0 & 1 & 0 \\
			& No license & Unknown & 0 & 3 & 3 \\
			& spdxBSD3 & AGPLv3+ & 0 & 0 & 2 \\
			\midrule
			\multicolumn{3}{l}{Total} &  79 & 77 & 202 \\
			\bottomrule
		\end{tabular} 
	}
\end{table}

%If developers copy and reuse these licensed pieces of code in their projects, conflicts may happen without their realisation.
In our study, we reveal another possible situation of software
licensing issues caused by code cloned to Stack Overflow. We found
evidence that 112 pieces of code have been copied from Qualitas
projects to Stack Overflow as examples. Their status of accepted
answers increase their chances of being reused. Even though most of
the Qualitas projects came with a software license, we found that the license information
were frequently missing after the code was copied to Stack
Overflow. The licensing terms on top of source code files are not
copied because usually only a small part of the file was
cloned. In overall, we can see that most of the Stack Overflow snippets do not
contain licensing terms while their clone counterparts in Qualitas
projects do. The summary of
licensing information is listed in \Cref{tab:license_abc}.

>>>>

\begin{table}[]
	\centering
	\caption{License mapping of  online clones (file-level)}
	\label{tab:license_abc}
	%\small
	\resizebox{\linewidth}{!}{
		\begin{tabular}{lp{2.2cm}lrrr}
			\toprule
			Type & Stack Overflow\newline (CC BY-NC-SA) & Qualitas & QS & EX & UD \\
			\midrule
			Compatible & No license & No license & 28 & & \\
			\midrule
			\multicolumn{3}{l}{Total} & 28 & & \\
			\midrule
			Incompat. & No license & Apache-2 & 55 & & \\
			          & No license & BSD-3 & 1 & & \\
			          & No license & CDDLorGPLv2 & 1 & & \\
			          & No license & EPLv1 & 19 & & \\
			          & No license & GPLv2+/3+ & 6 & & \\
			          & No license & LesserGPLv2.1+/3+ & 20 & & \\
			          & No license & Unknown & 24 & & \\
			\midrule
			\multicolumn{3}{l}{Total} & 154 & & \\
			\bottomrule
		\end{tabular} 
	}
\end{table}

%If developers copy and reuse these licensed pieces of code in their projects, conflicts may happen without their realisation.
In our study, we reveal another type of toxic code snippets which is software
licensing issues caused by code cloned to Stack Overflow. We found evidence that
154 pieces of code have been copied from Qualitas projects to Stack Overflow as
examples. Their status of accepted answers increase their chances of being
reused. Even though most of the Qualitas projects came with a software license,
we found that the license information were frequently missing after the code was
copied to Stack Overflow. The licensing terms on top of source code files are
not copied because usually only a small part of the file was cloned. In overall,
we can see that most of the Stack Overflow snippets do not contain licensing
terms while their clone counterparts in Qualitas projects do. The summary of
licensing information is listed in \Cref{tab:license_abc}.
